---
title: "Neuro_report"
format: html
embed-resources: true
editor: visual
---

## STEPCARE - REPORT2

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(here)
library(openxlsx)
library(reshape2)
library(tidyr)
library(readxl)
library(stringr)
library(here)
library(tableone)
library(knitr)
library(kableExtra)
library(purrr)
library(gtsummary)
library(gt)
library(flextable)
library(tidymodels)
library(broom)

## Read the other files. 
prep <- readRDS("/Users/josefdankiewicz/Library/CloudStorage/OneDrive-SharedLibraries-LundUniversity/cardiacarrest - Documents/STEPCARE/data/RDS/prep.rds")
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
##################################
## Neuromonitoring #############
##################################

# #1) Timepoint randomisation to prognostication <68 hours? (Y/N), if <68 h, 
# how many hours after randomisation was prognostication performed?

## Very high numbers over 120 ##
late_neuroprog <- prep %>% select(StudyPatientID,hours.to.prog) %>% filter(hours.to.prog>120)
## Low numbers over 120 ##
early_neuroprog <- prep %>% select(StudyPatientID,hours.to.prog) %>% filter(hours.to.prog<68)

proglist <- c("N_PROG_PoorPrognosis", "DIS_WLSTDecisionMade","DIS_ICStopReasonsBrainInjury","DIS_ICStopReasonsOrganFailure",
              "DIS_ICStopReasonsComorbidity","N_NSE48h","N_EEGHMalignant1st","N_CT_HIE1st","N_MRI_HIE1st",
              "N_N20AbsentBilateral","hours.to.death")

llist <- list()
for (i in 1:nrow(early_neuroprog)){
  k <- prep %>% select(StudyPatientID, all_of(proglist))
  k <- k %>% filter(StudyPatientID==early_neuroprog$StudyPatientID[i])
  names(k) <- c("ID","Poor prognossis", "WLST time","WLST reason: Brain","WLST reason: Organ Failure","WLST reason: Comorbidity",
                "NSE at 48h","EEG malignant (1st)","CT HIE","MRI HIE","N20 Absent", "Hours to death")
  k <- gather(k)
  k <- k %>% filter(!is.na(value))
  names(k) <- c(early_neuroprog$StudyPatientID[i], "variable")
  llist[[i]] <- k
}

names(llist) <- early_neuroprog$StudyPatientID

## Causes ##  


# 2) Timepoint randomisation to WLST cerebral causes < 68 h? If WLST neuro <68h, were there other causes for WLST such as ethical? 
early_wlst <- prep %>% filter(hours.to.wlst<68) %>% select(StudyPatientID,hours.to.wlst)

## Reasons for early WLST < 68h
wlst_reason <- prep %>% filter(hours.to.wlst<68) %>% select(StudyPatientID, DIS_ICStopReasonsBrainInjury,
                                                             DIS_ICStopReasonsOrganFailure, DIS_ICStopReasonsComorbidity,
                                                            DIS_ICStopReasonsOther,DIS_ICStopReasonsOtherSpecify)

names(wlst_reason) <- c("StudyPatientID","Brain injury","Organ failure","Comorbidity","Other","Other:Spec")

wlst_reason_brain <- prep %>% filter(hours.to.wlst<68) %>% select(StudyPatientID, DIS_ICStopReasonsBrainInjury,
                                                             DIS_ICStopReasonsOrganFailure, DIS_ICStopReasonsComorbidity,
                                                            DIS_ICStopReasonsOther,DIS_ICStopReasonsOtherSpecify,location_name) %>%
  filter(DIS_ICStopReasonsBrainInjury=="Yes") %>% filter(DIS_ICStopReasonsComorbidity=="No") %>% 
  filter(DIS_ICStopReasonsOrganFailure=="No") %>% select(StudyPatientID,DIS_ICStopReasonsOther,DIS_ICStopReasonsOtherSpecify,location_name)

names(wlst_reason_brain) <- c("StudyPatientID","Other reason for WLST","Other_Specify","Hospital")



#   Early-neuro:
#   3) Was a continuous EEG and/or routine EEG performed ≤32 hours after randomisation?
#   4) If no EEG (continuous or routine) was performed ≤32 h after randomisation, was any EEG performed after this timepoint? If so, how many hours after randomisation?

```

### Patients with a long time to prognostication
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(late_neuroprog, format="markdown")
```
### Patients with a short time to prognostication
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(early_neuroprog, format="markdown")
```
### Description of the patients with short times to prognostication
```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
## Need to include PRINT and AS.IS and CAT for a break in the loop ##
for (i in 1:nrow(early_neuroprog)){
print(kable(llist[[i]], format="markdown"))
  cat("\n")
}
```
## WLST
### Patients with short times to WLST
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(wlst_reason, format="markdown")
```
### Short WLST only neurological reasons
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(wlst_reason_brain, format="markdown")
```

# Early Neuro
###
If patient unconscious (FOUR-M <=3 at 48h), was a CT performed ≥20 h after randomisation?
```{r echo=FALSE, message=FALSE, warning=FALSE}
prep$time.to.ct1 <- as.numeric(prep$N_CTDateTime1st - prep$randomisation.datetime, units="hours")
prep$time.to.ct2 <- as.numeric(prep$N_CTDateTime2nd - prep$randomisation.datetime, units="hours")
prep$time.to.ct3 <- as.numeric(prep$N_CTDateTime3rd - prep$randomisation.datetime, units="hours")
prep$time.to.last.ct <- prep %>% select(c(time.to.ct1,time.to.ct2,time.to.ct3)) %>% pmap(pmax,na.rm=T) %>% as.numeric

prep$last.ct.after.20h <- ifelse(prep$time.to.last.ct>=20,"Yes","No")

prep$awake.at.48h <- ifelse(prep$hours.to.awakening>=48,"No","Yes") 

earlycheck1 <- prep %>% select(StudyPatientID, last.ct.after.20h,awake.at.48h) %>% 
  filter(awake.at.48h=="No") %>% arrange(last.ct.after.20h)

kable(earlycheck1, format="markdown")
```
###
If patient unconscious (FOUR-M <=3 at 48h), was any EEG performed ≥20 h after randomisation? (cEEG or full montage)
```{r echo=FALSE, message=FALSE, warning=FALSE}
prep$time.to.eeg.1st <- as.numeric(prep$N_EEGDateTime1st- prep$randomisation.datetime, units="hours")
prep$ceeg <- prep$N_cEEG


prep$eeg.before.36h <- ifelse(prep$time.to.eeg.1st<=36,"Yes","No")
prep$ceeg.or.eeg.before.36h <- ifelse(prep$ceeg=="Yes","Yes",prep$eeg.before.36h)

earlycheck2 <- prep %>% select(StudyPatientID, ceeg.or.eeg.before.36h,awake.at.48h) %>% filter(awake.at.48h=="No") %>% arrange(ceeg.or.eeg.before.36h)

kable(earlycheck2, format="markdown")
```
### For patients who were unconscious at 48h and did not have an eeg before 36h, did they have any eeg?
```{r echo=FALSE, message=FALSE, warning=FALSE}
yz <- earlycheck2 %>% filter(ceeg.or.eeg.before.36h=="No") %>% select(StudyPatientID)
earlycheck3 <- prep %>% filter(StudyPatientID %in% yz$StudyPatientID) %>% select(StudyPatientID,N_EEG1st,time.to.eeg.1st)

kable(earlycheck3, format="markdown")

```




